### 2018-08-07 paper/security-discussion.tex
Adds stub for device unlinkability
Adds discussion of bitwise unlinkability of C to security discussion

There are two changes that we have made that must be analysed.
We changed the key agreement from a pure \ac{DHKE}, \ie based on the \ac{DH} 
assumption, to one containing an indirection.
We also changed from the classical \ac{OR} of a fixed path with one node per 
layer to \ac{POR} with several nodes per layer.

The confidentiality of the key previously rested entirely on the \ac{DH} 
assumption (\(\alpha\) in the header).
Now it also rests on the security of the \ac{PRP} \(\prp'\) (\(C\) in the 
header).
The integrity is still reduced to the security of the \ac{MAC} \(\mac\) 
(\(\gamma\) in the header).

>>>>

There are two changes that we have made that must be analysed.
We changed the key agreement from a pure \ac{DHKE}, \ie based on the \ac{DH} 
assumption, to one containing an indirection.
We also changed from the classical \ac{OR} of a fixed path with one node per 
layer to a set of alternative nodes per layer.

The first change:
The confidentiality of the key previously rested entirely on the \ac{DH} 
assumption (\(\alpha\) in the header).
Now it also rests on the security of the \ac{PRP} \(\prp'\) (\(C\) in the 
header).
The integrity is still reduced to the security of the \ac{MAC} \(\mac\) 
(\(\gamma\) in the header).
We still achieve the bitwise unlinkability since \(C\) is replaced at each 
layer and the next \(C\) is hidden inside the header --- which otherwise 
remains identical to that of Sphinx.
